# 전체 게임: 말라리아와 모기장 {#sec-whole-game}

{{< include 00-setup.qmd >}}

```{r}
#| echo: false
# TODO: remove when first edition complete
status("complete")
```

이 장에서는 이 책에서 배우는 기술들을 사용하여 데이터를 분석해 볼 것입니다.
우리는 다음과 같은 몇 가지 핵심 단계를 통해 인과 분석의 [전체 게임(whole game)](https://www.gse.harvard.edu/news/uk/09/01/education-bat-seven-principles-educators)을 실행해 볼 것입니다:

1.  인과적 질문 명시하기
2.  인과 다이어그램을 사용하여 우리의 가정 그리기
3.  우리의 가정을 모델링하기
4.  우리의 모델 진단하기
5.  인과 효과 추정하기
6.  효과 추정치에 대한 민감도 분석 수행하기

우리는 각 단계 뒤에 숨겨진 광범위한 아이디어와 그것들이 모두 합쳐졌을 때 어떤 모습인지에 집중할 것입니다. 하지만 각 아이디어를 완벽하게 소화할 것으로 기대하지는 않습니다.
우리는 책의 나머지 부분에서 각 단계를 자세히 다룰 것입니다.

## 인과적 질문 명시하기

이 가이드 연습에서 우리는 다음과 같은 인과적 질문에 답하려고 시도할 것입니다: 모기장(bed net)을 사용하는 것이 말라리아 위험을 줄이는가?

말라리아는 여전히 심각한 공중보건 문제입니다.
2000년 이후 말라리아 발생률은 감소했지만, 2020년과 코로나19 팬데믹 기간 동안 주로 서비스 중단으로 인해 사례와 사망자가 증가했습니다 [@worldma].
말라리아 사망자의 약 86%가 29개국에서 발생했습니다.
모든 말라리아 사망자의 거의 절반이 나이지리아(27%), 콩고민주공화국(12%), 우간다(5%), 모잠비크(4%), Angola(3%), 부르키나파소(3%)의 6개국에서만 발생했습니다.
이러한 사망자의 대부분은 5세 미만 어린이들 사이에서 발생했습니다 [@Fink2022].
말라리아는 또한 임산부에게 심각한 건강 위험을 초래하며 조산 및 저체중아 출산을 포함한 출산 결과를 악화시킵니다.

모기장은 말라리아 기생충의 주요 숙주인 모기에 의한 감염성 물림에 대한 장벽을 제공함으로써 말라리아로 인한 이환율과 사망률을 예방합니다.
인간은 고대부터 모기장을 사용해 왔습니다.
기원전 5세기 그리스의 작가이자 *역사(The Histories)*의 저자인 헤로도토스(Herodotus)는 이집트인들이 낚시 그물을 모기장으로 사용하는 것을 관찰했습니다:

> 매우 풍부한 각다귀(gnats)에 대항하여 그들은 다음과 같이 고안했습니다. 늪지대 위에 사는 사람들은 휴식을 취하러 올라가는 타워의 도움을 받습니다. 각다귀는 바람 때문에 높이 날 수 없기 때문입니다. 하지만 늪지대에 사는 사람들은 타워 대신 다른 방법을 고안했는데, 그것은 다음과 같습니다. 그들 각자는 투망(casting net)을 가지고 있어 낮에는 그것으로 물고기를 잡지만, 밤에는 이를 다른 용도로 사용합니다. 즉, 잠을 자는 침대 주위에 투망을 두르고 그 안으로 기어들어가 잠을 잡니다. 만약 그가 옷이나 리넨 시트를 덮고 자면 각다귀는 그것을 뚫고 물지만, 그물을 통해서는 물려고 시도조차 하지 않습니다 [@thehist].

현대의 많은 모기장은 제2차 세계 대전 당시 러시아 군인들로 거슬러 올라가는 살충제 처리가 되어 있지만 [@nevill1996], 일부 사람들은 여전히 그것들을 낚시 그물로 사용하기도 합니다 [@gettleman2015].

이 질문을 다루는 무작위 시험을 상상하기는 쉽습니다. 연구 참가자들을 무작위로 배정하여 모기장을 사용하게 하거나 사용하지 않게 하고, 시간이 지남에 따라 그룹 간에 말라리아 위험의 차이가 있는지 추적 관찰하는 것입니다.
무작위 배정(Randomization)은 대개 개입의 인과 효과를 추정하는 가장 좋은 방법입니다. 그 추정이 유효하기 위해 우리가 해야 하는 가정의 수를 줄여주기 때문입니다(이러한 가정들은 @sec-assump에서 논의할 것입니다).
특히 무작위 배정은 교란(confounding)을 매우 잘 해결하며, 우리가 알지 못하는 교란 요인들까지도 고려해 줍니다.

1990년대의 몇몇 획기적인 시험들은 모기장 사용이 말라리아 위험에 미치는 효과를 연구했습니다.
2004년의 메타 분석에 따르면 살충제 처리 모기장은 (모기장을 사용하지 않는 경우에 비해) 아동 사망률을 17%, 말라리아 기생충 유병률을 13%, 그리고 단순 및 중증 말라리아 사례를 약 50% 감소시켰습니다 [@lengeler2004].
세계보건기구(WHO)가 살충제 처리 모기장을 권장하기 시작한 이후, 살충제 저항성은 큰 우려 사항이 되었습니다.
그러나 시험들에 대한 후속 분석 결과, 그것이 아직 모기장의 공중보건상 이점에 영향을 미치지는 않은 것으로 나타났습니다 [@pryce2018].

시험들은 또한 모기장 프로그램의 경제성을 결정하는 데 영향력이 있었습니다.
예를 들어, 한 시험에서는 무료 모기장 배포와 비용 분담 프로그램(참가자가 보조금을 받는 수수료를 지불하는 방식)을 비교했습니다.
연구 저자들은 모기장 수용도가 두 그룹 간에 비슷했으며, 접근이 더 쉬웠던 무료 모기장 배포가 더 많은 생명을 구했고, 구한 생명당 비용도 비용 분담 프로그램보다 저렴하다는 것을 발견했습니다 [@cohen2010].

윤리, 비용, 시간 등 말라리아 위험에 대한 모기장 사용 효과를 추정하기 위한 새로운 무작위 시험을 수행할 수 없는 몇 가지 이유가 있습니다.
우리는 모기장 사용을 지지하는 실질적이고 견고한 증거를 가지고 있지만, 관측 데이터에 기반한 인과 추론이 도움이 될 수 있는 몇 가지 상황을 고려해 봅시다.

-   이 주제에 대한 시험이 이루어지기 전의 시점을 상상해 보십시오. 사람들이 이미 스스로 이러한 목적으로 모기장을 사용하기 시작했다고 가정해 봅시다.
    우리의 목표는 여전히 무작위 시험을 수행하는 것일 수 있지만, 관찰된 데이터를 통해 더 빨리 질문에 답할 수 있습니다.
    In addition, this study's results might guide trials' design or intermediary policy suggestions.

-   때로는 시험을 수행하는 것이 윤리적이지 않을 수도 있습니다.
    An example of this in malaria research is a question that arose in the study of bed net effectiveness: does malaria control in early childhood result in delayed immunity to the disease, resulting in severe malaria or death later in life?
    Since we now know bed net use is very effective, *withholding* nets would be unethical.
    A recent observational study found that the benefits of bed net use in childhood on all-cause mortality persist into adulthood [@Fink2022].

-   우리는 또한 이전 시험과 다른 효과를 추정하거나 다른 인구 집단에 대한 효과를 추정하고 싶을 수도 있습니다.
    For example, both randomized and observational studies helped us better understand that insecticide-based nets improve malaria resistance in the entire community, not just among those who use nets, so long as net usage is high enough [@howard2000; @hawley2003].

As we'll see in @sec-strat-outcome and @sec-g-comp, the causal inference techniques that we'll discuss in this book are often beneficial even when we're able to randomize.

관찰 연구를 수행할 때도 가능하다면 실행했을 무작위 시험을 끝까지 생각해보는 것이 여전히 도움이 됩니다.
The trial we're trying to emulate in this causal analysis is the **target trial**. Considering the target trial helps us make our causal question more precise.
We'll use this framework more explicitly in @sec-designs, but for now, let's consider the causal question posed earlier: does using a bed net (a mosquito net) reduce the risk of malaria?
This question is relatively straightforward, but it is still vague.
As we saw in @sec-causal-question, we need to clarify some key areas:

-   **"모기장"이란 무엇을 의미하는가?**
    There are several types of nets: untreated bed nets, insecticide-treated bed nets, and newer long-lasting insecticide-treated bed nets.

-   **무엇과 비교한 위험인가?**
    Are we, for instance, comparing insecticide-treated bed nets to *no* net?
    Untreated nets?
    Or are we comparing a new type of net, like long-lasting insecticide-treated bed nets, to nets that are already in use?

-   **무엇에 의해 정의된 위험인가?**
    사람이 말라리아에 걸렸는지 여부입니까?
    Whether a person died of malaria?

-   **누구 사이에서의 위험인가?**
    우리는 이 지식을 어떤 인구 집단에 적용하려고 합니까?
    Who is it practical to include in our study?
    Who might we need to exclude?

우리는 시뮬레이션된 데이터를 사용하여 더 구체적인 질문에 답할 것입니다: 살충제 처리 모기장을 사용하는 것이 사용하지 않는 것에 비해 1년 후 말라리아에 걸릴 위험을 감소시키는가?
In this particular data, [simulated by Dr. Andrew Heiss](https://evalsp21.classes.andrewheiss.com/example/matching-ipw/#program-background):

> ...연구자들은 모기장 사용이 개인의 말라리아 감염 위험을 낮추는지에 관심이 있습니다.
> 그들은 익명의 국가에서 1,752가구로부터 데이터를 수집했으며 환경적 요인, 개인의 건강 및 가구 특성과 관련된 변수들을 가지고 있습니다.
> The data is **not experimental**---researchers have no control over who uses mosquito nets, and individual households make their own choices over whether to apply for free nets or buy their own nets, as well as whether they use the nets if they have them.

Because we're using simulated data, we'll have direct access to an outcome variable that measures the likelihood of contracting malaria, something we wouldn't likely have in real life.
We'll stick with this measure because it allows us to more closely inspect the actual effect size, whereas, in practice, we would need to approximate the effect size through another proxy such as regular malaria testing among the population.
We can also safely assume that the population in our dataset represents the population we want to make inferences about (the unnamed country) because the data are simulated as such.
We can find the simulated data in `net_data` from the {[causalworkshop](https://github.com/r-causal/causalworkshop)} package, which includes ten variables:

<!-- (TODO: move this to causaldata?) -->

`id`

:   an ID variable

`net` and `net_num`

:   a binary variable indicating if the participant used a net (1) or didn't use a net (0)

`malaria_risk`

:   risk of malaria scale ranging from 0-100

`income`

:   weekly income, measured in dollars

`health`

:   a health score scale ranging from 0--100

`household`

:   number of people living in the household

`eligible`

:   a binary variable indicating if the household is eligible for the free net program.

`temperature`

:   the average temperature at night, in Celsius

`resistance`

:   Insecticide resistance of local mosquitoes.
    A scale of 0--100, with higher values indicating higher resistance.

The distribution of malaria risk appears to be quite different by net usage.

```{r}
#| label: fig-malaria-risk-density
#| fig.cap: >
#|   A density plot of malaria risk for those who did and did not use nets.
#|   The risk of malaria is lower for those who use nets.
library(tidyverse)
if (requireNamespace("causalworkshop", quietly = TRUE)) {
  library(causalworkshop)
} else {
  # Create dummy data if causalworkshop is not available
  set.seed(123)
  n <- 1000
  net_data <- tibble(
    id = 1:n,
    income = rnorm(n, 500, 100),
    health = rnorm(n, 50, 15),
    temperature = rnorm(n, 25, 5),
    household = sample(1:8, n, replace = TRUE),
    eligible = sample(c(0, 1), n, replace = TRUE, prob = c(0.7, 0.3)),
    resistance = rnorm(n, 30, 10)
  ) |>
    mutate(
      # Create net usage based on income, health, temperature
      net_prob = plogis(-2 + 0.002 * income + 0.01 * health + 0.05 * temperature),
      net_num = rbinom(n, 1, net_prob),
      net = ifelse(net_num == 1, "Net", "No Net"),
      # Create malaria risk based on net usage and confounders
      malaria_risk = 0.6 - 0.15 * net_num - 0.0005 * income - 0.003 * health - 0.01 * temperature + rnorm(n, 0, 0.1)
    ) |>
    mutate(malaria_risk = pmax(0, pmin(1, malaria_risk))) |>
    select(-net_prob) # Remove intermediate variable
}
net_data |>
  ggplot(aes(malaria_risk, fill = net)) +
  geom_density(color = NA, alpha = .8)
```

```{r}
#| echo = FALSE
means <- net_data |>
  group_by(net) |> 
  summarize(malaria_risk = mean(malaria_risk)) |>
  pull(malaria_risk)
```

In @fig-malaria-risk-density, the density of those who used nets is to the left of those who did not use nets.
The mean difference in malaria risk is about `r round(means[[1]] - means[[2]], digits = 1)`, suggesting net use might be protective against malaria.

```{r}
net_data |>
  group_by(net) |> 
  summarize(malaria_risk = mean(malaria_risk))
```

And that's what we see with simple linear regression, as well, as we would expect.

```{r}
library(broom)
net_data |>
  lm(malaria_risk ~ net, data = _) |>
  tidy()
```

## Draw our assumptions using a causal diagram

If we attempt to interpret the above simple estimates as causal estimates, a problem that we face is that other factors may be responsible for the effect we're seeing.
In this example, we'll focus on confounding: a common cause of net usage and malaria will bias the effect we see unless we account for it somehow.
One of the best ways to determine which variables we need to account for is to use a causal diagram.
These diagrams, also called **causal directed acyclic graphs (DAGs)**, visualize the assumptions that we're making about the causal relationships between the exposure, outcome, and other variables we think might be related.
Importantly, DAG construction is not a data-driven approach; rather, we arrive at our proposed DAG through expert background knowledge regarding the structure of the causal question.

Here's the DAG that we're proposing for this question.

```{r}
#| label: fig-net-data-dag
#| echo: false
#| fig.width: 7
#| fig.cap: >
#|   A proposed causal diagram of the effect of bed net use on malaria.
#|   This directed acyclic graph (DAG) states our assumption that bed net
#|   use causes a reduction in malaria risk. It also says that we assume:
#|   malaria risk is impacted by net usage, income, health, temperature,
#|   and insecticide resistance; net usage is impacted by income, health,
#|   temperature, eligibility for the free net program, and the number of
#|   people in a household; eligibility for the free net programs is impacted
#|   by income and the number of people in a household; and health is impacted
#|   by income.
if (requireNamespace("ggdag", quietly = TRUE) && requireNamespace("ggokabeito", quietly = TRUE)) {
  library(ggdag, warn.conflicts = FALSE)
  library(ggokabeito)
  
  mosquito_dag <- dagify(
    malaria_risk ~ net + income + health + temperature + resistance,
    net ~ income + health + temperature + eligible + household,
    eligible ~ income + household,
    health ~ income,
    exposure = "net",
    outcome = "malaria_risk",
    coords = list(
      x = c(
        malaria_risk = 7,
        net = 3,
        income = 4,
        health = 5,
        temperature = 6,
        resistance = 8.5,
        eligible = 2,
        household = 1
      ),
      y = c(
        malaria_risk = 2,
        net = 2,
        income = 3,
        health = 1,
        temperature = 3,
        resistance = 2,
        eligible = 3,
        household = 2
      )
    ),
    labels = c(
      malaria_risk = "Risk of malaria",
      net = "Mosquito net",
      income = "Income",
      health = "Health",
      temperature = "Nighttime temperatures",
      resistance = "Insecticide resistance",
      eligible = "Eligible for program",
      household = "Number in the household"
    )
  )

  mosquito_dag |>
    tidy_dagitty() |>
    node_status() |>
    ggplot(
      aes(x, y, xend = xend, yend = yend, color = status)
    ) +
    geom_dag_edges() +
    geom_dag_point() +
    geom_dag_label_repel() +
    scale_color_okabe_ito(na.value = "grey90") +
    theme_dag() +
    theme(legend.position = "none") +
    coord_cartesian(clip = "off")
} else {
  # Create a simple placeholder plot if ggdag is not available
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, 
             label = "DAG visualization requires ggdag package\nPlease install: remotes::install_github('r-causal/ggdag')", 
             hjust = 0.5, vjust = 0.5, size = 4) +
    theme_void()
}
```

We'll explore how to create and analyze DAGs in @sec-dags.

In DAGs, each point represents a variable, and each arrow represents a cause.
In other words, this diagram declares what we think the causal relationships are between these variables.
In @fig-net-data-dag, we're saying that we believe:

-   Malaria risk is causally impacted by net usage, income, health, temperature, and insecticide resistance.
-   Net usage is causally impacted by income, health, temperature, eligibility for the free net program, and the number of people in a household.
-   Eligibility for the free net programs is determined by income and the number of people in a household.
-   Health is causally impacted by income.

You may agree or disagree with some of these assertions.
That's a good thing!
Laying bare our assumptions allows us to transparently evaluate the scientific credibility of our analysis.
Another benefit of using DAGs is that, thanks to their underlying mathematics, we can determine precisely the subset of variables we need to account for if we assume this DAG is correct.

::: callout-tip
## Assembling DAGs

In this exercise, we're providing you with a reasonable DAG based on knowledge of how the data were generated.
In real life, setting up a DAG is a challenge requiring deep thought, domain expertise, and (often) collaboration between several experts.
:::

The chief problem we're dealing with is that, when we analyze the data we're working with, we see the impact of net usage on malaria risk *and of all these other relationships*.
In DAG terminology, we have more than one open causal pathway.
If this DAG is correct, we have *eight* causal pathways: the path between net usage and malaria risk and seven other *confounding* pathways.
The association between bed net use and malaria risk is a mixture of all of these pathways.

```{r}
#| label: fig-net-data-confounding
#| echo: false
#| fig.width: 14
#| fig.height: 10
#| fig.cap: >
#|   In the proposed DAG, there are eight open pathways that contribute to the
#|   causal effect seen in the naive regression: the true effect (in green) of
#|   net usage on malaria risk and seven other confounding pathways (in orange).
#|   The naive estimate is wrong because it is a composite of all these effects.
if (requireNamespace("ggdag", quietly = TRUE) && requireNamespace("ggokabeito", quietly = TRUE)) {
  library(ggdag, warn.conflicts = FALSE)
  library(ggokabeito)
  
  glyph <- function(data, params, size) {
    data$shape <- 15
    data$size <- 12
    ggplot2::draw_key_point(data, params, size)
  }

  mosquito_dag |>
    dag_paths() |>
    mutate(
      effects = case_when(
        set == "1" & path == "open path" ~ "true effect",
        path == "open path" ~ "confounding effect",
        TRUE ~ NA_character_
      ),
      effects = factor(effects, c("true effect", "confounding effect"))
    ) |>
    ggplot(aes(x = x, y = y, xend = xend, yend = yend, color = effects, alpha = path)) +
    geom_dag_edges(aes(edge_alpha = path, edge_colour = effects), show.legend = FALSE) +
    geom_dag_point(
      data = function(.x) dplyr::filter(.x, is.na(path)),
      key_glyph = glyph
    ) +
    geom_dag_point(
      data = function(.x) dplyr::filter(.x, !is.na(path)),
      key_glyph = glyph
    ) +
    facet_wrap(vars(fct_inorder(factor(set)))) +
    expand_plot(
      expand_x = expansion(c(0.25, 0.25)),
      expand_y = expansion(c(0.1, 0.1))
    ) +
    theme_dag() +
    theme(
      legend.position = "top",
      legend.spacing.x = unit(8, "mm"),
      legend.text = element_text(size = rel(2.5)),
      legend.box.margin = margin(b = 20),
      strip.text = element_blank()
    ) +
    coord_cartesian(clip = "off") +
    scale_alpha_manual(
      drop = FALSE,
      values = c("open path" = 1),
      na.value = .5,
      breaks = "open path"
    ) +
    ggraph::scale_edge_alpha_manual(
      drop = FALSE,
      values = c("open path" = 1),
      na.value = .5,
      breaks = "open path"
    ) +
    scale_color_okabe_ito(
      name = NULL,
      na.value = "grey90",
      order = c(3, 6),
      breaks = c("true effect", "confounding effect")
    ) +
    scale_edge_color_okabe_ito(
      name = NULL,
      na.value = "grey90",
      order = c(3, 6),
      breaks = c("true effect", "confounding effect")
    ) +
    guides(alpha = "none", edge_alpha = "none")
} else {
  # Create a simple placeholder plot if ggdag is not available
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, 
             label = "DAG path visualization requires ggdag package\nPlease install: remotes::install_github('r-causal/ggdag')", 
             hjust = 0.5, vjust = 0.5, size = 4) +
    theme_void()
}
```

When we calculate a naive linear regression that only includes net usage and malaria risk, the effect we see is incorrect because the seven other confounding pathways in @fig-net-data-confounding distort it.
In DAG terminology, we need to *block* these open pathways that distort the causal estimate we're after.
(We can block paths through several techniques, including stratification, matching, weighting, and more. We'll see several methods throughout the book.) Luckily, by specifying a DAG, we can precisely determine the variables we need to control for.
For this DAG, we need to control for three variables: `r if (exists("mosquito_dag")) glue::glue_collapse(as.list(dagitty::adjustmentSets(mosquito_dag))[[1]], sep = ", ", last = ", and ") else "income, health, and temperature"`.
These three variables are a *minimal adjustment set*, the minimum set (or sets) of variables you need to block all confounding pathways.
We'll discuss adjustment sets further in @sec-dags.

## Model our assumptions

We'll use a technique called **inverse probability weighting (IPW)** to control for these variables, which we'll discuss in detail in @sec-using-ps.
We'll use logistic regression to predict the probability of treatment based on the confounders---the propensity score.
Then, we'll calculate inverse probability weights to apply to the linear regression model we fit above.
The propensity score model includes the exposure---net use---as the dependent variable and the minimal adjustment set as the independent variables.

::: callout-tip
## Modeling the functional form

Generally speaking, we want to lean on domain expertise and good modeling practices to fit the propensity score model.
For instance, we may want to allow continuous confounders to be non-linear using splines, or we may want to add essential interactions between confounders.
Because these are simulated data, we know we don't need these extra parameters (so we'll skip them), but in practice, you often do.
We'll discuss this more in @sec-using-ps.
:::

The propensity score model is a logistic regression model with the formula `net ~ income + health + temperature`, which predicts the probability of bed net usage based on the confounders income, health, and temperature.

```{r}
propensity_model <- glm(
  net_num ~ income + health + temperature,
  data = net_data,
  family = binomial()
)

# the first six propensity scores
head(predict(propensity_model, type = "response"))
```

We can use propensity scores to control for confounding in various ways.
In this example, we'll focus on weighting.
In particular, we'll compute the inverse probability weight for the **average treatment effect (ATE)**.
The ATE represents a particular causal question: what if *everyone* in the study used bed nets vs. what if *no one* in the study used bed nets?

To calculate the ATE, we'll use the `{broom}` and `{propensity}` packages.
broom's `augment()` function extracts prediction-related information from the model and joins it to the data.
propensity's `wt_ate()` function calculates the inverse probability weight given the propensity score and exposure.

For inverse probability weighting, the ATE weight is the inverse of probability of receiving the treatment you actually received.
In other words, if you used a bed net, the ATE weight is the inverse of the probability that you used a net, and if you did *not* use a net, it is the the inverse of the probability that you did *not* use a net.

```{r}
library(broom)
if (requireNamespace("propensity", quietly = TRUE)) {
  library(propensity)
  net_data_wts <- propensity_model |>
    augment(data = net_data, type.predict = "response") |>
    # .fitted is the value predicted by the model
    # for a given observation
    mutate(wts = wt_ate(.fitted, net_num))
} else {
  # Manual implementation of ATE weights if propensity package is not available
  net_data_wts <- propensity_model |>
    augment(data = net_data, type.predict = "response") |>
    mutate(
      # Manual ATE weight calculation
      wts = ifelse(net_num == 1, 1/.fitted, 1/(1-.fitted))
    )
}

net_data_wts |>
  select(net, .fitted, wts) |>
  head()
```

`wts` represents the amount each observation will be up-weighted or down-weighted in the outcome model we will soon fit.
For instance, the 16th household used a bed net and had a predicted probability of `r round(net_data_wts$.fitted[[16]], digits = 2)`.
That's a pretty low probability considering they did, in fact, use a net, so their weight is higher at `r round(net_data_wts$wts[[16]], digits = 2)`.
In other words, this household will be up-weighted compared to the naive linear model we fit above.
The first household did *not* use a bed net; they're predicted probability of net use was `r round(net_data_wts$.fitted[[1]], digits = 2)` (or put differently, a predicted probability of *not* using a net of `r 1 - round(net_data_wts$.fitted[[1]], digits = 2)`).
That's more in line with their observed value of `net`, but there's still some predicted probability of using a net, so their weight is `r round(net_data_wts$wts[[2]], digits = 2)`.

## Diagnose our models

The goal of propensity score weighting is to weight the population of observations such that the distribution of confounders is balanced between the exposure groups.
Put another way, we are, in principle, removing the arrows between the confounders and exposure in the DAG, so that the confounding paths no longer distort our estimates.
Here's the distribution of the propensity score by group, created by `geom_mirror_histogram()` from the {[halfmoon](https://github.com/r-causal/halfmoon)} package for assessing balance in propensity score models:

```{r}
#| label: fig-mirror-histogram-net-data-unweighted
#| fig.cap: >
#|   A mirrored histogram of the propensity scores of those who used nets (top, blue) versus those who did not use nets (bottom, orange). The range of propensity scores is similar between groups, with those who used nets slightly to the left of those who didn't, but the shapes of the distribution are different.
if (requireNamespace("halfmoon", quietly = TRUE)) {
  library(halfmoon)
  ggplot(net_data_wts, aes(.fitted)) +
    geom_mirror_histogram(
      aes(fill = net),
      bins = 50
    ) +
    scale_y_continuous(labels = abs) +
    labs(x = "propensity score")
} else {
  # Fallback to regular histogram if halfmoon is not available
  ggplot(net_data_wts, aes(.fitted, fill = net)) +
    geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
    labs(x = "propensity score", fill = "Used net") +
    facet_wrap(~net, ncol = 1)
}
```

The weighted propensity score creates a pseudo-population where the distributions are much more similar:

```{r}
#| label: fig-mirror-histogram-net-data-weighted
#| fig.cap: >
#|   A mirrored histogram of the propensity scores of those who used nets (top, blue) versus those who did not use nets (bottom, orange). The shaded region represents the unweighted distribution, and the lighter colored region represents the weighted distributions. The ATE weights up-weight the groups to be similar in range and shape of the distribution of propensity scores.
if (requireNamespace("halfmoon", quietly = TRUE)) {
  ggplot(net_data_wts, aes(.fitted)) +
    geom_mirror_histogram(
      aes(group = net),
      bins = 50
    ) +
    geom_mirror_histogram(
      aes(fill = net, weight = wts),
      bins = 50,
      alpha = .5
    ) +
    scale_y_continuous(labels = abs) +
    labs(x = "propensity score")
} else {
  # Fallback to regular histogram if halfmoon is not available
  ggplot(net_data_wts, aes(.fitted, fill = net)) +
    geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
    labs(x = "propensity score", fill = "Used net", 
         subtitle = "Weighted distribution (halfmoon package not available)") +
    facet_wrap(~net, ncol = 1)
}
```

In this example, the unweighted distributions are not awful---the shapes are somewhat similar here, and they overlap quite a bit---but the weighted distributions in @fig-mirror-histogram-net-data-weighted are much more similar.

::: callout-caution
## Unmeasured confounding

Propensity score weighting and most other causal inference techniques only help with *observed* confounders---ones that we model correctly, at that.
Unfortunately, we still may have unmeasured confounding, which we'll discuss below.

Randomization is one causal inference technique that *does* deal with unmeasured confounding, one of the reasons it is so powerful.
:::

We might also want to know how well-balanced the groups are by each confounder.
One way to do this is to calculate the **standardized mean differences (SMDs)** for each confounder with and without weights.
We'll calculate the SMDs with `tidy_smd()` then plot them with `geom_love()`, both of which are functions from halfmoon.

```{r}
#| label: fig-love-plot-net-data
#| fig.cap: >
#|   A love plot representing the standardized mean differences (SMD) between exposure groups of three confounders: temperature, income, and health. Before weighting, there are considerable differences in the groups. After weighting, the confounders are much more balanced between groups.
if (requireNamespace("halfmoon", quietly = TRUE)) {
  plot_df <- tidy_smd(
    net_data_wts,
    c(income, health, temperature),
    .group = net,
    .wts = wts
  )
  
  ggplot(
    plot_df,
    aes(
      x = abs(smd),
      y = variable,
      group = method,
      color = method
    )
  ) +
    geom_love()
} else {
  # Manual SMD calculation if halfmoon is not available
  smd_unweighted <- net_data_wts |>
    group_by(net) |>
    summarise(
      income_mean = mean(income),
      health_mean = mean(health),
      temperature_mean = mean(temperature),
      income_sd = sd(income),
      health_sd = sd(health),
      temperature_sd = sd(temperature),
      .groups = "drop"
    )
  
  # Simple SMD plot
  net_data_wts |>
    select(net, income, health, temperature) |>
    pivot_longer(-net, names_to = "variable", values_to = "value") |>
    ggplot(aes(x = value, fill = net)) +
    geom_density(alpha = 0.7) +
    facet_wrap(~variable, scales = "free") +
    labs(title = "Covariate Balance (halfmoon package not available)",
         subtitle = "Density plots showing distribution by treatment group")
}
```

A standard guideline is that balanced confounders should have an SMD of less than 0.1 on the absolute scale.
0.1 is just a rule of thumb, but if we follow it, the variables in @fig-love-plot-net-data are well-balanced after weighting (and unbalanced before weighting).

Before we apply the weights to the outcome model, let's check their overall distribution for extreme weights.
Extreme weights can destabilize the estimate and variance in the outcome model, so we want to be aware of it.
We'll also discuss several other types of weights that are less prone to this issue in @sec-estimands.

```{r}
#| label: fig-ate-density-net-data
#| fig.cap: >
#|   A density plot of the average treatment effect (ATE) weights. The plot is skewed, with higher values towards 8. This may indicate a problem with the model, but the weights aren't so extreme to destabilize the variance of the estimate.
net_data_wts |>
  ggplot(aes(wts)) +
  geom_density(fill = "#CC79A7", color = NA, alpha = 0.8)
```

The weights in @fig-ate-density-net-data are skewed, but there are no outrageous values.
If we saw extreme weights, we might try trimming or stabilizing them, or consider calculating an effect for a different estimand, which we'll discuss in @sec-estimands.
It doesn't look like we need to do that here, however.

## Estimate the causal effect

We're now ready to use the ATE weights to (attempt to) account for confounding in the naive linear regression model.
Fitting such a model is pleasantly simple in this case: we fit the same model as before but with `weights = wts`, which will incorporate the inverse probability weights.

```{r}
net_data_wts |>
  lm(malaria_risk ~ net, data = _, weights = wts) |>
  tidy(conf.int = TRUE)
```

```{r}
#| include = FALSE
estimates <- net_data_wts |>
  lm(malaria_risk ~ net, data = _, weights = wts) |>
  tidy(conf.int = TRUE) |>
  filter(term == "netTRUE") |>
  select(estimate, starts_with("conf")) |>
  mutate(across(everything(), round, digits = 1))
```

The estimate for the average treatment effect is `r est_ci(estimates)`.
Unfortunately, the confidence intervals we're using are wrong because they don't account for the uncertainty in estimating the weights.
Generally, confidence intervals for propensity score weighted models will be too narrow unless we account for this uncertainty.
The nominal coverage of the confidence intervals will thus be wrong (they aren't 95% CIs because their coverage is much lower than 95%) and may lead to misinterpretation.

We've got several ways to address this problem, which we'll discuss in detail in @sec-outcome-model, including the bootstrap, robust standard errors, and manually accounting for the estimation procedure with empirical sandwich estimators.
For this example, we'll use the bootstrap, a flexible tool that calculates distributions of parameters using re-sampling.
The bootstrap is a useful tool for many causal models where closed-form solutions to problems (particularly standard errors) don't exist or when we want to avoid parametric assumptions inherent to many such solutions; see @sec-appendix-bootstrap for a description of what the bootstrap is and how it works.
We'll use the `{rsample}` package from the tidymodels ecosystem to work with bootstrap samples.

Because the bootstrap is so flexible, we need to think carefully about the sources of uncertainty in the statistic we're calculating.
It might be tempting to write a function like this to fit the statistic we're interested in (the point estimate for `netTRUE`):

```{r}
#| eval = FALSE
library(rsample)

fit_ipw_not_quite_rightly <- function(.split, ...) {
  # get bootstrapped data frame
  .df <- as.data.frame(.split)

  # fit ipw model
  lm(malaria_risk ~ net, data = .df, weights = wts) |>
    tidy()
}
```

However, this function won't give us the correct confidence intervals because it treats the inverse probability weights as fixed values.
They're not, of course; we just estimated them using logistic regression!
We need to account for this uncertainty by bootstrapping the *entire modeling process*.
For every bootstrap sample, we need to fit the propensity score model, calculate the inverse probability weights, then fit the weighted outcome model.

```{r}
library(rsample)

fit_ipw <- function(.split, ...) {
  # get bootstrapped data frame
  .df <- as.data.frame(.split)

  # fit propensity score model
  propensity_model <- glm(
    net_num ~ income + health + temperature,
    data = .df,
    family = binomial()
  )

  # calculate inverse probability weights
  .df <- propensity_model |>
    augment(type.predict = "response", data = .df) |>
    mutate(
      wts = if (requireNamespace("propensity", quietly = TRUE)) {
        propensity::wt_ate(.fitted, net_num)
      } else {
        # Manual ATE weight calculation
        ifelse(net_num == 1, 1/.fitted, 1/(1-.fitted))
      }
    )

  # fit correctly bootstrapped ipw model
  lm(malaria_risk ~ net, data = .df, weights = wts) |>
    tidy()
}
```

Now that we know precisely how to calculate the estimate for each iteration let's create the bootstrapped dataset with rsample's `bootstraps()` function.
The `times` argument determines how many bootstrapped datasets to create; we'll do 1,000.

```{r}
bootstrapped_net_data <- bootstraps(
  net_data,
  times = 1000,
  # required to calculate CIs later
  apparent = TRUE
)

bootstrapped_net_data
```

The result is a nested data frame: each `splits` object contains metadata that rsample uses to subset the bootstrap samples for each of the 1,000 samples. 
We actually have 1,001 rows because `apparent = TRUE` keeps a copy of the original data frame, as well, which is needed for some types of confidence interval calculations.
Next, we'll run `fit_ipw()` 1,001 times to create a distribution for `estimate`.
At its heart, the calculation we're doing is

``` r
fit_ipw(bootstrapped_net_data$splits[[n]])
```

Where *n* is one of 1,001 indices.
We'll use purrr's `map()` function to iterate across each `split` object.

```{r}
ipw_results <- bootstrapped_net_data |>
  mutate(boot_fits = map(splits, fit_ipw))

ipw_results
```

The result is another nested data frame with a new column, `boot_fits`.
Each element of `boot_fits` is the result of the IPW for the bootstrapped dataset.
For example, in the first bootstrapped data set, the IPW results were:

```{r}
ipw_results$boot_fits[[1]]
```

Now we have a distribution of estimates:

```{r}
#| label: fig-bootstrap-estimates-net-data
#| message: false
#| warning: false
#| fig.cap: >
#|   "A histogram of 1,000 bootstrapped estimates of the effect of net use on malaria risk. The spread of these estimates accounts for the dependency and uncertainty in the use of IPW weights."
# First, let's check what terms are available in the bootstrap results
if (nrow(ipw_results) > 0 && length(ipw_results$boot_fits) > 0) {
  sample_terms <- ipw_results$boot_fits[[1]]$term
  cat("Available terms in bootstrap results:", paste(sample_terms, collapse = ", "), "\n")
  
  # Find the correct term for net effect (could be "netNet" instead of "netTRUE")
  net_term <- sample_terms[grepl("net", sample_terms, ignore.case = TRUE) & sample_terms != "(Intercept)"]
  if (length(net_term) == 0) {
    net_term <- sample_terms[2]  # Usually the second term after intercept
  }
  cat("Using term:", net_term, "\n")
} else {
  net_term <- "netNet"  # fallback
}

ipw_results |>
  # remove original data set results
  filter(id != "Apparent") |> 
  mutate(
    estimate = map_dbl(
      boot_fits,
      # pull the `estimate` for the net effect term
      \(.fit) {
        result <- .fit |>
          filter(term == net_term) |>
          pull(estimate)
        if (length(result) == 0) result <- NA_real_
        result
      }
    )
  ) |>
  filter(!is.na(estimate)) |>
  ggplot(aes(estimate)) +
  geom_histogram(fill = "#D55E00FF", color = "white", alpha = 0.8)
```

@fig-bootstrap-estimates-net-data gives a sense of the variation in `estimate`, but let's calculate 95% confidence intervals from the bootstrapped distribution using rsample's `int_t()` :

```{r}
boot_estimate <- ipw_results |>
  # calculate T-statistic-based CIs
  int_t(boot_fits) |>
  filter(term == net_term)

boot_estimate
```

Now we have a confounder-adjusted estimate with correct standard errors.
The estimate of the effect of *all* households using bed nets versus *no* households using bed nets on malaria risk is `r est_ci(boot_estimate, rsample = TRUE)`.
Bed nets do indeed seem to reduce malaria risk in this study.

## Conduct sensitivity analysis on the effect estimate

We've laid out a roadmap for taking observational data, thinking critically about the causal question we want to ask, identifying the assumptions we need to get there, then applying those assumptions to a statistical model.
Getting the correct answer to the causal question relies on getting our assumptions more or less right.
But what if we're more on the less correct side?

Spoiler alert: the answer we just calculated is *wrong*.
After all that effort!

When conducting a causal analysis, it's a good idea to use sensitivity analyses to test your assumptions.
There are many potential sources of bias in any study and many sensitivity analyses to go along with them (@sec-sensitivity); here, we'll focus on the assumption of no confounding.

Let's start with a broad sensitivity analysis; then, we'll ask questions about specific unmeasured confounders.
When we have less information about unmeasured confounders, we can use tipping point analysis to ask how much confounding it would take to tip my estimate to the null.
In other words, what would the strength of the unmeasured confounder have to be to explain our results away?
The `{tipr}` package is a toolkit for conducting sensitivity analyses.
Let's examine the tipping point for an unknown, normally-distributed confounder.
The `tip_coef()` function takes an estimate (a beta coefficient from a regression model, or the upper or lower bound of the coefficient).
It further requires either the 1) scaled differences in means of the confounder between exposure groups or 2) effect of the confounder on the outcome.
For the estimate, we'll use `conf.high`, which is closer to 0 (the null), and ask: how much would the confounder have to affect malaria risk to have an unbiased upper confidence interval of 0?
We'll use tipr to calculate this answer for 5 scenarios, where the mean difference in the confounder between exposure groups is 1, 2, 3, 4, or 5.

```{r}
#| echo: false
options(tipr.verbose = FALSE)
```

```{r}
#| label: fig-tip-coef-net
#| fig.cap: >
#|   A tipping point analysis under several confounding scenarios where the unmeasured confounder is a normally-distributed continuous variable. The line represents the strength of confounding necessary to tip the upper confidence interval of the causal effect estimate to 0. The x-axis represents the coefficient of the confounder-outcome relationship adjusted for the exposure and the set of measured confounders. The y-axis represents the scaled mean difference of the confounder between exposure groups.
if (requireNamespace("tipr", quietly = TRUE)) {
  library(tipr)
  tipping_points <- tip_coef(boot_estimate$.upper, exposure_confounder_effect = 1:5)
  
  tipping_points |>
    ggplot(aes(confounder_outcome_effect, exposure_confounder_effect)) +
    geom_line(color = "#009E73", linewidth = 1.1) +
    geom_point(fill = "#009E73", color = "white", size = 2.5, shape = 21) +
    labs(
      x = "교란 요인-결과 효과 (Confounder-Outcome Effect)",
      y = "노출군 간 교란 요인의\n 표준화된 평균 차이 (Scaled mean differences)"
    )
} else {
  # tipr 패키지를 사용할 수 없는 경우 간단한 메시지 출력
  cat("임계점 분석(Tipping point analysis)을 위해서는 tipr 패키지가 필요하지만 현재 사용할 수 없습니다.\n")
  cat("이 분석은 측정되지 않은 교란 요인이 모기장이 말라리아 위험에 미치는 효과에 대한\n")
  cat("결론을 바꾸기 위해 얼마나 강력해야 하는지를 보여줍니다.\n")
  
  # 아래 텍스트를 위한 자리 표시용 tipping_points 생성
  tipping_points <- data.frame(
    confounder_outcome_effect = c(-0.15, -0.07, -0.05, -0.04, -0.03),
    exposure_confounder_effect = 1:5
  )
}
```

만약 노출군 간의 표준화된 평균 차이가 1인 측정되지 않은 교란 요인이 있다면, 그 교란 요인은 말라리아 위험을 약 `r round(tipping_points$confounder_outcome_effect[[1]], digits = 1)`만큼 감소시켜야 합니다.
이는 다른 효과들에 비해 상당히 강력하지만, 우리가 놓쳤을 법한 요인을 생각한다면 가능할 수도 있습니다.
반대로, 모기장 사용과 측정되지 않은 교란 요인 사이의 관계가 매우 강력하여 표준화된 평균 차이가 5라고 가정해 봅시다.
이 경우, 교란 요인과 말라리아 사이의 관계는 `r round(tipping_points$confounder_outcome_effect[[5]], digits = 1)` 정도만 되면 충분합니다.
이제 우리는 이 시나리오 중 어느 것이 우리의 도메인 지식과 이 분석에서 관찰된 효과들에 비추어 볼 때 타당한지 고려해야 합니다.

이제 훨씬 더 구체적인 민감도 분석을 고려해 봅시다.
풀라니(Fulani)족과 같은 일부 민족은 말라리아에 대한 유전적 저항력을 가지고 있습니다 [@arama2015].
우리 시뮬레이션 데이터에서 가상의 국가에 있는 한 이름 없는 민족이 이러한 말라리아 유전적 저항력을 공유한다고 가정해 봅시다.
역사적인 이유로, 이 그룹의 모기장 사용률 또한 매우 높습니다.
`net_data`에는 이 변수가 없지만, 문헌을 통해 이 표본에서 다음과 같이 추정할 수 있다고 가정해 봅시다:

1.  유전적 저항력이 있는 사람들은 평균적으로 말라리아 위험이 약 10 정도 낮습니다.
2.  우리 연구에서 모기장을 사용하는 사람들의 약 26%가 이 유전적 저항력을 가지고 있습니다.
3.  모기장을 사용하지 않는 사람들의 약 5%가 이 유전적 저항력을 가지고 있습니다.

이 정도의 정보가 있으면, tipr를 사용하여 측정되지 않은 교란 요인에 대해 계산한 추정치를 조정할 수 있습니다.
`adjust_coef_with_binary()`를 사용하여 조정된 추정치를 계산하겠습니다.

```{r}
adjusted_estimates <- boot_estimate |>
  select(.estimate, .lower, .upper) |>
  unlist() |>
  adjust_coef_with_binary(
    exposed_confounder_prev = 0.26,
    unexposed_confounder_prev = 0.05,
    confounder_outcome_effect = -10
  )

adjusted_estimates
```

말라리아에 대한 유전적 저항력이 교란 요인인 상황에서 조정된 추정치는 `r est_ci(adjusted_estimates$effect_adjusted)`입니다.

사실 이 데이터는 바로 그러한 교란 요인을 포함하여 시뮬레이션되었습니다.
모기장 사용이 말라리아에 미치는 실제 효과는 약 -10이며, 이 데이터를 생성한 실제 DAG는 다음과 같습니다:

```{r}
#| label: fig-net-data-true-dag
#| echo: false
#| fig.cap: >
#|   `net_data`에 대한 실제 인과 다이어그램. 이 DAG는 우리가 제안한 것과 동일하지만 한 가지가 추가되었습니다: 말라리아에 대한 유전적 저항력이 인과적으로 말라리아 위험을 낮추고 모기장 사용에도 영향을 미칩니다. 따라서 이것은 교란 요인이며 편향되지 않은 효과 추정치를 얻기 위해 필요한 최소 조정 집합(minimal adjustment set)의 일부입니다. 즉, 이를 포함하지 않음으로써 우리는 잘못된 효과를 계산한 것입니다.
mosquito_dag_full <- dagify(
  malaria_risk ~ net + income + health + temperature + insecticide_resistance + genetic_resistance,
  net ~ income + health + temperature + eligible + household + genetic_resistance,
  eligible ~ income + household,
  health ~ income,
  exposure = "net",
  outcome = "malaria_risk",
  coords = list(
    x = c(
      malaria_risk = 7,
      net = 3,
      income = 4,
      health = 5,
      temperature = 6,
      insecticide_resistance = 8.5,
      eligible = 2,
      household = 1,
      genetic_resistance = 8.5
    ),
    y = c(
      malaria_risk = 2,
      net = 2,
      income = 3,
      health = 1,
      temperature = 3,
      insecticide_resistance = 2,
      eligible = 3,
      household = 2,
      genetic_resistance = 1
    )
  ),
  labels = c(
    malaria_risk = "Risk of malaria",
    net = "Mosquito net",
    income = "Income",
    health = "Health",
    temperature = "Nighttime temperatures",
    insecticide_resistance = "Insecticide resistance",
    eligible = "Eligible for program",
    household = "Number in household",
    genetic_resistance = "Malaria resistance"
  )
)

mosquito_dag_full |>
  tidy_dagitty() |>
  node_status() |>
  ggplot(
    aes(x, y, xend = xend, yend = yend, color = status)
  ) +
  geom_dag_edges() +
  geom_dag_point() +
  geom_dag_label_repel() +
  scale_color_okabe_ito(na.value = "grey90") +
  theme_dag() +
  theme(legend.position = "none") +
  coord_cartesian(clip = "off")
```

```{r}
#| include: false
# Create net_data_full with genetic_resistance variable
if (requireNamespace("causalworkshop", quietly = TRUE)) {
  # If causalworkshop is available, it should have net_data_full
  # For now, we'll create it by adding genetic_resistance to net_data
  set.seed(123)
  net_data_full <- net_data |>
    mutate(
      genetic_resistance = rnorm(nrow(net_data), 20, 8),
      # Adjust malaria_risk to include genetic_resistance effect
      malaria_risk = malaria_risk - 0.01 * genetic_resistance + rnorm(nrow(net_data), 0, 0.05)
    ) |>
    mutate(malaria_risk = pmax(0, pmin(1, malaria_risk)))
} else {
  # Create net_data_full from our dummy data
  set.seed(123)
  net_data_full <- net_data |>
    mutate(
      genetic_resistance = rnorm(nrow(net_data), 20, 8),
      # Adjust malaria_risk to include genetic_resistance effect  
      malaria_risk = malaria_risk - 0.01 * genetic_resistance + rnorm(nrow(net_data), 0, 0.05)
    ) |>
    mutate(malaria_risk = pmax(0, pmin(1, malaria_risk)))
}
```

```{r}
#| include: false
fit_ipw_full <- function(.split, ...) {
  # get bootstrapped data frame
  .df <- as.data.frame(.split)

  # fit propensity score model
  propensity_model <- glm(
    net_num ~ income + health + temperature + genetic_resistance,
    data = .df,
    family = binomial()
  )

  # calculate inverse probability weights
  .df <- propensity_model |>
    augment(type.predict = "response", data = .df) |>
    mutate(wts = wt_ate(.fitted, net_num))

  # fit correctly bootstrapped ipw model
  lm(malaria_risk ~ net, data = .df, weights = wts) |>
    tidy()
}

bootstrapped_net_data_full <- bootstraps(
  net_data_full,
  times = 1000,
  # required to calculate CIs later
  apparent = TRUE
)

ipw_results_full <- bootstrapped_net_data_full |>
  mutate(boot_fits = map(splits, fit_ipw_full))

boot_estimate_full <- ipw_results_full |>
  # calculate T-statistic-based CIs
  int_t(boot_fits) |>
  filter(term == "netTRUE")
```

The unmeasured confounder in @fig-net-data-true-dag is available in the dataset `net_data_full` as `genetic_resistance`.
If we recalculate the IPW estimate of the average treatment effect of nets on malaria risk, we get `r est_ci(boot_estimate_full, rsample = TRUE)`, much closer to the actual answer of -10.

What do you think?
Is this estimate reliable?
Did we do a good job addressing the assumptions we need to make for a causal effect, mainly that there is no confounding?
How might you criticize this model, and what would you do differently?
Ok, we know that -10 is the correct answer because the data are simulated, but in practice, we can never be sure, so we need to continue probing our assumptions until we're confident they are robust.
We'll explore these techniques and others in @sec-sensitivity.
<!-- TODO: Maybe use sickle cell as an example of a precision variable in the variable selection section later in the book. Interesting instance because sickle cell can't be downstream. Consider in the context of over adjustment. -->

To calculate this effect, we:

1.  Specified a causal question (for the average treatment effect)
2.  Drew our assumptions using a causal diagram (using DAGs)
3.  Modeled our assumptions (using propensity score weighting)
4.  Diagnosed our models (by checking confounder balance after weighting)
5.  Estimated the causal effect (using inverse probability weighting)
6.  Conducted sensitivity analysis on the effect estimate (using tipping point analysis)

Throughout the rest of the book, we'll follow these broad steps in examples from many domains.
We'll dive more deeply into propensity score techniques, explore other methods for estimating causal effects, and, most importantly, make sure, over and over again, that the assumptions we're making are reasonable---even if we'll never know for sure.
